Formalizing Stack Safety as a Security Property

### 2023-01-05 submission5/core.tex
Added that paragraph about the factorization

>>>>

This approach has several benefits: first, not all state-safety enforcement mechanisms
aim to protect all aspects of stack safety. Most protect control flow, but relatively
few care about the confidentiality of the callee after return. Second, our formalism
factors stack safety into three questions: (1) ``when does this machine call, return, etc.?''
(2) ``during any given call, which elements of the state are in need of protection?'' and
(3) ``when an element needs protection, how can we tell that it is protected?''
Different machines, including those with different enforcement mechanisms, may answer question
(1) differently, without needing new definitions for (2) or (3). In order to adjust our notion
of permissible behavior to correspond to features such as pass-by-reference behavior, which
alter its security requirements (typically by relaxing them), we need only add nuance to (2).
Regardless of the assumptions that we make for either (1) or (2), the security definitions that
answer (3) need not change.
